Notes for 9/16/19 - 9/20/19

### 2021-09-01 notes/weekly_notes/9.16.19.NotesForWeek.tex
Added a bunch of notes.

\documentclass{report}
\usepackage{amsmath}
\usepackage{amsfonts, amsthm, amssymb}
\usepackage{graphicx}
\usepackage[colorlinks]{hyperref}
\usepackage[parfill]{parskip}
\usepackage{algpseudocode}
\usepackage{algorithm}
\usepackage{enumerate}
\usepackage[shortlabels]{enumitem}
\usepackage{fullpage}
\usepackage{mathtools}
\usepackage{subcaption}
\usepackage{tikz}

@@

\DeclareFontFamily{U}{mathx}{\hyphenchar\font45}
\DeclareFontShape{U}{mathx}{m}{n}{<-> mathx10}{}
\DeclareSymbolFont{mathx}{U}{mathx}{m}{n}
\DeclareMathAccent{\wb}{0}{mathx}{"73}

\DeclarePairedDelimiterX{\norm}[1]{\lVert}{\rVert}{#1}

\newcommand{\eqdist}{\ensuremath{\stackrel{d}{=}}}
\newcommand{\Graph}{\mathcal{G}}
\newcommand{\Reals}{\mathbb{R}}
\newcommand{\Identity}{\mathbb{I}}
\newcommand{\Xsetistiid}{\overset{\text{i.i.d}}{\sim}}
\newcommand{\convprob}{\overset{p}{\to}}
\newcommand{\convdist}{\overset{w}{\to}}
\newcommand{\Expect}[1]{\mathbb{E}\left[ #1 \right]}
\newcommand{\Risk}[2][P]{\mathcal{R}_{#1}\left[ #2 \right]}
\newcommand{\Prob}[1]{\mathbb{P}\left( #1 \right)}
\newcommand{\iset}{\mathbf{i}}
\newcommand{\jset}{\mathbf{j}}
\newcommand{\myexp}[1]{\exp \{ #1 \}}
\newcommand{\abs}[1]{\left \lvert #1 \right \rvert}
\newcommand{\restr}[2]{\ensuremath{\left.#1\right|_{#2}}}
\newcommand{\ext}[1]{\widetilde{#1}}
\newcommand{\set}[1]{\left\{#1\right\}}
\newcommand{\seq}[1]{\set{#1}_{n \in \N}}
\newcommand{\Xsetotp}[2]{\langle #1, #2 \rangle}
\newcommand{\floor}[1]{\left\lfloor #1 \right\rfloor}
\newcommand{\Var}{\mathrm{Var}}
\newcommand{\Cov}{\mathrm{Cov}}
\newcommand{\Xsetiam}{\mathrm{diam}}

\newcommand{\emC}{C_n}
\newcommand{\emCpr}{C'_n}
\newcommand{\emCthick}{C^{\sigma}_n}
\newcommand{\emCprthick}{C'^{\sigma}_n}
\newcommand{\emS}{S^{\sigma}_n}
\newcommand{\estC}{\widehat{C}_n}
\newcommand{\hC}{\hat{C^{\sigma}_n}}
\newcommand{\vol}{\mathrm{vol}}
\newcommand{\spansp}{\mathrm{span}~}
\newcommand{\1}{\mathbf{1}}

\newcommand{\Linv}{L^{\Xsetagger}}
\DeclareMathOperator*{\argmin}{argmin}
\DeclareMathOperator*{\argmax}{argmax}

\newcommand{\emF}{\mathbb{F}_n}
\newcommand{\emG}{\mathbb{G}_n}
\newcommand{\emP}{\mathbb{P}_n}
\newcommand{\F}{\mathcal{F}}
\newcommand{\D}{\mathcal{D}}
\newcommand{\R}{\mathcal{R}}
\newcommand{\Rd}{\Reals^d}
\newcommand{\Nbb}{\mathbb{N}}

%%% Vectors
\newcommand{\thetast}{\theta^{\star}}
\newcommand{\betap}{\beta^{(p)}}
\newcommand{\betaq}{\beta^{(q)}}
\newcommand{\vardeltapq}{\varDelta^{(p,q)}}

%%% Matrices
\newcommand{\X}{X} % no bold
\newcommand{\Y}{Y} % no bold
\newcommand{\Z}{Z} % no bold
\newcommand{\Lgrid}{L_{\grid}}
\newcommand{\Xsetgrid}{D_{\grid}}
\newcommand{\Linvgrid}{L_{\grid}^{\Xsetagger}}
\newcommand{\Lap}{{\bf L}}
\newcommand{\NLap}{{\bf N}}
\newcommand{\PLap}{{\bf P}}

%%% Sets and classes
\newcommand{\Xset}{\mathcal{X}}
\newcommand{\Sset}{\mathcal{S}}
\newcommand{\Hclass}{\mathcal{H}}
\newcommand{\Pclass}{\mathcal{P}}
\newcommand{\Leb}{L}
\newcommand{\mc}[1]{\mathcal{#1}}

%%% Distributions and related quantities
\newcommand{\Pbb}{\mathbb{P}}
\newcommand{\Ebb}{\mathbb{E}}
\newcommand{\Qbb}{\mathbb{Q}}
\newcommand{\Ibb}{\mathbb{I}}

%%% Operators
\newcommand{\Tadj}{T^{\star}}
\newcommand{\Xsetive}{\mathrm{div}}
\newcommand{\Xsetif}{\mathop{}\!\mathrm{d}}
\newcommand{\gradient}{\mathcal{D}}
\newcommand{\Hessian}{\mathcal{D}^2}
\newcommand{\dotp}[2]{\langle #1, #2 \rangle}
\newcommand{\Dotp}[2]{\Bigl\langle #1, #2 \Bigr\rangle}

%%% Misc
\newcommand{\grid}{\mathrm{grid}}
\newcommand{\critr}{R_n}
\newcommand{\Xsetx}{\,dx}
\newcommand{\Xsety}{\,dy}
\newcommand{\Xsetr}{\,dr}
\newcommand{\Xsetxpr}{\,dx'}
\newcommand{\Xsetypr}{\,dy'}
\newcommand{\wt}[1]{\widetilde{#1}}
\newcommand{\wh}[1]{\widehat{#1}}
\newcommand{\ol}[1]{\overline{#1}}
\newcommand{\spec}{\mathrm{spec}}
\newcommand{\LE}{\mathrm{LE}}
\newcommand{\LS}{\mathrm{LS}}
\newcommand{\OS}{\mathrm{OS}}
\newcommand{\PLS}{\mathrm{PLS}}
\newcommand{\dist}{\mathrm{dist}}

@@

\begin{document}
\title{Work for revision of ``Local Spectral Clustering of Density Upper Level Sets''}
\author{Alden Green}
\date{\today}
\maketitle

\chapter{Normalized cut}
To recall, our upper bound on normalized cut---ignoring the terms that depend on the density---is 
\begin{equation*}
\wt{\Phi}_{\nu,r}(\mc{C}_{\sigma}) \lessapprox \frac{16dr}{9\sigma}.
\end{equation*}
\section{Lower bound on normalized cut}
Our goal is to examine the tightness of our upper bound on normalized cut (Theorem 10 of our JMLR submission), by giving a comparable lower bound. Recall that the (uniform, population level) normalized cut of a set $\mc{C}_{\sigma}$ is given by
\begin{equation*}
\Phi_{\nu,r}(\mc{C}_{\sigma}) := \frac{\int_{\mc{C}_{\sigma}} \nu(B(x,r) \setminus \mc{C}_{\sigma}) \,dx}{\int_{\mc{C}_{\sigma}} \nu(B(x,r)) \,dx}.
\end{equation*}
As informed by the isoperimetric ratio, the worst-case for a functional like normalized cut should be when $\mc{C}_{\sigma}$ by a $d$-dimensional ball. Letting $\mc{C}_{\sigma} = B(0,\sigma)$, we have that
\begin{equation*}
\frac{\int_{\mc{C}_{\sigma}} \nu(B(x,r) \setminus \mc{C}_{\sigma}) \,dx}{\int_{\mc{C}_{\sigma}} \nu(B(x,r)) \,dx} = \frac{1}{\nu_d^2 r^d \sigma^d} \int_{\mc{C}_{\sigma}} \nu(B(x,r) \setminus \mc{C}_{\sigma}) \,dx.
\end{equation*}
If $\|x\| < \sigma - r$, then $B(x,r) \setminus \mc{C}_{\sigma} = \emptyset$. Otherwise $\sigma - r \leq \|x\| \leq \sigma$, and if $r \ll \sigma$ then $B(x,r) \setminus \mc{C}_{\sigma} \approx \mathrm{cap}_{r}(\|x\| - (\sigma - r))$. Converting to polar coordinates, we have:
\begin{align*}
\int_{\mc{C}_{\sigma}} \nu(B(x,r) \setminus \mc{C}_{\sigma}) \,dx & \approx s_d \int_{\sigma - r}^{\sigma} \nu(\mathrm{cap}_{r}(x - (\sigma - r))) t^{d - 1} \,dt \\
& \geq s_d (\sigma - r)^{d - 1} \int_{\sigma - r}^{\sigma} \nu(\mathrm{cap}_{r}(t - (\sigma - r)))  \,dt \\
& = s_d (\sigma - r)^{d - 1} \int_{0}^{r} \nu(\mathrm{cap}_{r}(z)  \,dz.
\end{align*}
As calculated below~\eqref{eqn:lb_conductance_1}, $\int_{0}^{r} \nu(\mathrm{cap}_{r}(z)  \,dz = \frac{1}{d + 1} \nu_d r^{d + 1} \frac{\Gamma(d/2 + 1)}{\Gamma(d/2 + 1/2)\sqrt{\pi}} \approx \frac{1}{d + 1} \nu_d r^{d + 1} \frac{\sqrt{d + 2}}{\sqrt{2\pi}}$ and hence
\begin{equation*}
\Phi_{\nu,r}(\mc{C}_{\sigma}) \approx s_d (\sigma - r)^{d - 1}\frac{1}{d + 1} \nu_d r^{d + 1} \frac{\sqrt{d + 2}}{\sqrt{2\pi}} \frac{1}{\nu_d^2 r^d \sigma^d} \approx \frac{ \sqrt{d + 2}}{(d + 1)\sqrt{2\pi}} \cdot \frac{dr}{\sigma}.
\end{equation*}
By contrast, our upper bound is $\approx dr/\sigma$, revealing a gap of roughly $\frac{ \sqrt{d + 2}}{(d + 1)\sqrt{2\pi}}$.

\chapter{Lower bound for conductance of continuous-space ball walk}
For $x \in \mc{C}_{\sigma}$ and measurable $\Sset \subseteq \mc{C}_{\sigma}$, let $\ell_{\nu,r}(x) = \nu(B(x,r) \cap \mc{C}_{\sigma})$ and ${J}_{\nu,r}(\mc{S}) = \int_{\mc{S}} \ell_{\nu,r}(x) \,dx$. Further define
\begin{equation*}
\widetilde{P}_{\nu,r}(x; \Sset) := \frac{\nu(\Sset \cap B(x,r))}{\nu(\mc{C}_{\sigma} \cap B(x,r))}, \quad \widetilde{\pi}_{\nu,r}(\Sset) = \frac{J_{\nu,r}(\mc{S})}{J_{\nu,r}(\mc{C}_{\sigma})}, \quad  \widetilde{Q}_{\nu,r}(\Sset_1,\Sset_2) := \int_{\Sset_1} \widetilde{P}_{\nu,r}(x;\Sset_2) \,d\widetilde{\pi}_{\nu,r}(x).
\end{equation*}
The uniform continuous normalized cut and conductance are then
\begin{equation*}
\widetilde{\Phi}_{\nu,r}(\Sset) := \frac{\widetilde{Q}_{\nu,r}(\Sset, \Sset^c)}{\min\set{\widetilde{\pi}_{\nu,r}(\Sset),\widetilde{\pi}_{\nu,r}(\Sset^c)}}, \quad \widetilde{\Phi}_{\nu,r} := \min_{\Sset \subseteq \mc{C}_{\sigma}} \widetilde{\Phi}_{\nu,r}(\Sset),
\end{equation*}
where the minimum is taken over all measurable sets $\Sset \subseteq \mc{C}_{\sigma}$.

\begin{lemma}
	\label{lem: uniform_continuous_conductance}
	Let $\mc{C}_{\sigma}$ satisfy Assumption \textcolor{red}{(A3)} (of our main document) for some convex set $\mathcal{K}$ with diameter $\rho$, and measure-preserving mapping $g: \mathcal{K} \to \mc{C}_{\sigma}$ with Lipschitz constant $L$. Let $0 < \ell < 1/2$ be a number that satisfies $\ell_{\nu,r}(x) \geq \nu_d r^d \ell$ for all $x \in \mc{C}_{\sigma}$.  Then the uniform conductance $\widetilde{\Phi}_{\nu,r}$ is lower bounded:
	\begin{equation*}
	\widetilde{\Phi}_{\nu,r} \geq \Bigl(1 - \frac{r}{4\rho}\Bigr) \cdot\frac{\ell^2\sqrt{2\pi}}{9} \cdot \frac{r}{\rho L \sqrt{d + 2}}
	\end{equation*}
\end{lemma}
Lemma~\ref{lem: overlap_balls} gives the lower bound $\ell \geq 1/2 \cdot (1 - r/\sigma \cdot \sqrt{(d + 2)/(2\pi)})$ leading to the following corollary.
\begin{corollary}
	\label{cor: uniform_continuous_conductance}
	Let $\mc{C}_{\sigma}$ satisfy Assumption \textcolor{red}{(A3)} for some convex set $\mathcal{K}$ with diameter $\rho$, and measure-preserving mapping $g: \mathcal{K} \to \mc{C}_{\sigma}$ with Lipschitz constant $L$. Then the uniform conductance $\widetilde{\Phi}_{\nu,r}$ is lower bounded:
	\begin{equation*}
	\widetilde{\Phi}_{\nu,r} \geq \Bigl(1 - \frac{r}{4\rho}\Bigr) \Bigl(1 - \frac{r}{\sigma}\sqrt{\frac{d + 2}{2\pi}}\Bigr)^2 \cdot \frac{\sqrt{2\pi}}{36} \cdot \frac{r}{\rho L \sqrt{d + 2}}
	\end{equation*}
\end{corollary}

\subsection{Proof of Lemma~\ref{lem: uniform_continuous_conductance}}
Lower bounds on the conductance of geometric random walks follow a typical pattern, in which one supplies an isoperimetric inequality, uses this to lower bound the ergodic flow $\wt{Q}$, and thereby derives a lower bound on the conductance. The proof of Lemma~\ref{lem: uniform_continuous_conductance} proceeds along these lines, and we start by sketching the chain of inequalities we will use. For a given partition $\{\mc{S},\mc{R}\}$ of $\mc{C}_{\sigma}$, write
\begin{equation*}
\mc{S}^{\delta} := \biggl\{u \in \mc{S}: \wt{P}(u,\mc{R}) \leq \delta \biggr\}~~\textrm{and}~~\mc{R}^{\delta} := \biggl\{u \in \mc{R}: \wt{P}(u,\mc{S}) \leq \delta \biggr\} 
\end{equation*}
where $\delta$ is a small number we will determine later on. Let $\mc{S}_{\delta} := \mc{C}_{\sigma} \setminus (\mc{S}^{\delta} \cup \mc{R}^{\delta})$. 
\begin{enumerate}
	\item[1.] The ergodic flow $\wt{Q}$ between $\mc{S}$ and $\mc{R}$ satisfies the following lower bound:
	\begin{equation*}
	\wt{Q}_{\nu,r}(\mc{S},\mc{R}) \geq \frac{1}{2} \wt{\pi}_{\nu,r}(\mc{S}_{\delta}) \cdot \delta.
	\end{equation*}
	\item[2.] For any $\mc{S} \subseteq \mc{C}_{\sigma}$, it holds that
	\begin{equation*}
	\frac{\nu(\mc{S})}{\nu(\mc{C}_{\sigma})} \cdot \ell \leq \wt{\pi}_{\nu,r}(\mc{S}) \leq \frac{\nu_d r^d \nu(\mc{S})}{I(\mc{C}_{\sigma})}
	\end{equation*}
	\item[3.] From \textcolor{red}{Abbasi-Yadkori} (see also the seminal works of \textcolor{red}{(Lovasz and Simonovits)} and \textcolor{red}{(Dyer)}), we have the following isoperimetric inequality.
	\begin{lemma}[Isoperimetry of Lipschitz embeddings of convex sets.]
		\label{lem: nonconvex_isoperimetry}
		Let $\mc{C}_{\sigma}$ satisfy Assumption \textcolor{red}{(A3)} for some convex set $\mathcal{K}$ with diameter $\rho$, and measure-preserving mapping $g: \mathcal{K} \to \mc{C}_{\sigma}$ with Lipschitz constant $L$. Then, for any partition $(\Omega_1,\Omega_2,\Omega_3)$ of $\mc{C}_{\sigma}$, 
		\begin{equation*}
		\nu(\Omega_3) \geq 2\frac{\dist(\Omega_1, \Omega_2)}{\rho L} \min(\nu(\Omega_1), \nu(\Omega_2)).
		\end{equation*}
	\end{lemma}
	\item[4.] 
	The following Lemma relates the Euclidean distance $\|x - y\|$ to the the total variation distance
	\begin{equation*}
	\|\wt{P}(x,\cdot) - \wt{P}(y,\cdot)\|_{\mathrm{TV}} = \sup_{\mc{S} \subseteq \mc{C}_{\sigma}} |\wt{P}(x,\mc{S}) - \wt{P}(y,\mc{S}) |
	\end{equation*}
	\begin{lemma}
		\label{lem: one_step_distributions}
		For all $x,y \in \mc{C}_{\sigma}$ and any $\mc{S} \in \mc{C}_{\sigma}$, it holds that
		\begin{equation}
		\label{eqn:one_step_distributions_1}
		\|x - y\| \geq \Bigl(\bigl|\wt{P}(x,\mc{S}) - \wt{P}(y,\mc{S})\bigr|\Bigr)\sqrt{\frac{2\pi}{d + 2}}r\ell
		\end{equation}
		Therefore, for any $\mc{S}_1,\mc{S}_2 \subseteq \mc{C}_{\sigma}$, it holds that
		\begin{equation}
		\label{eqn:one_step_distributions_2}
		\dist(\mc{S}_1,\mc{S}_2) \geq \Bigl(\inf_{\substack{x \in \mc{S}_1 \\ y \in \mc{S}_2}}\|\wt{P}(x,\cdot) - \wt{P}(y,\cdot)\|_{\mathrm{TV}}\Bigr)\sqrt{\frac{2\pi}{d + 2}}r\ell.
		\end{equation}
	\end{lemma}
	Note that for any $x \in \mc{S}^{\delta}, y \in \mc{R}^{\delta}$, we have that
	\begin{equation*}
	\wt{P}(x,\mc{S}) - \wt{P}(y,\mc{S}) = 1 - \bigl(\wt{P}(x,\mc{R}) + \wt{P}(y,\mc{S})\bigr) \geq 1 - 2\delta,
	\end{equation*}
	Thus, applying Lemma~\ref{lem: one_step_distributions} to $\mc{S}^{\delta}$ and $\mc{R}^{\delta}$ gives
	\begin{equation*}
	\dist(\mc{S}^{\delta},\mc{R}^{\delta}) \geq \bigl(1 - 2\delta\bigr) \cdot \sqrt{\frac{2\pi}{d + 2}}r\ell
	\end{equation*}
\end{enumerate}
The claim of Lemma~\ref{lem: uniform_continuous_conductance}---i.e. a lower bound on the continuous normalized cut $\wt{\Phi}_{\nu,r}(\mc{S})$ that holds for any measurable $\mc{S} \subseteq \mc{C}_{\sigma}$---directly follows from these inequalities, as we now show. In particular, the ergodic flow $\wt{Q}(\mc{S},\mc{R})$ can be lower bounded
\begin{equation*}
\wt{Q}_{\nu,r}(\mc{S},\mc{R}) \geq \frac{1}{2}\wt{\pi}_{\nu,r}(\mc{S}_{\delta}) \cdot \delta. \tag{Step 1}
\end{equation*}
Now, suppose $\wt{\pi}_{\nu,r}(\mc{S}^{\delta}) \leq (1 - a) \wt{\pi}_{\nu,r}(\mc{S})$ or $\wt{\pi}_{\nu,r}(\mc{R}^{\delta}) \leq (1 - a) \wt{\pi}_{\nu,r}(\mc{R})$, for some $0 < a < 1$. Then $\wt{\pi}_{\nu,r}(\mc{S}_{\delta}) \geq a \min\{\wt{\pi}_{\nu,r}(\mc{S}),\wt{\pi}_{\nu,r}(\mc{R})\}$, and consequently,
\begin{equation*}
\wt{\Phi}_{\nu,r}(\mc{S}) = \frac{\wt{Q}_{\nu,r}(\mc{S},\mc{S}^c)}{\min\{\wt{\pi}_{\nu,r}(\mc{S}),\wt{\pi}_{\nu,r}(\mc{R})\}} \geq \frac{1}{2}a \delta.
\end{equation*}
Otherwise, we deduce that
\begin{align*}
\wt{Q}_{\nu,r}(\mc{S},\mc{R}) & \geq \frac{\nu(\mc{S}_{\delta})\nu_dr^d}{2I(\mc{C}_{\sigma})} \cdot \ell \delta \tag{Step 2} \\
& \geq \frac{\dist(\mc{S}^{\delta},\mc{R}^{\delta})}{\rho L} \frac{\nu_dr^d\min\{\nu(\mc{S}^{\delta}),\nu(\mc{R}^{\delta})\}}{J(\mc{C}_{\sigma})}  \ell^2 \delta \tag{Step 3}\\
& \geq \frac{r (1 - 2\delta)\sqrt{2\pi}}{\rho L\sqrt{d + 2}} \frac{\nu_dr^d \min\{\nu(\mc{S}^{\delta}),\nu(\mc{R}^{\delta})\}}{J(\mc{C}_{\sigma})}  \ell^2 \delta \tag{Step 4} \\
& \geq  \frac{r (1 - 2\delta)\sqrt{2\pi}}{\rho L\sqrt{d + 2}} \min\bigl\{\wt{\pi}_{\nu,r}(\mc{S}^{\delta}),\wt{\pi}_{\nu,r}(\mc{R}^{\delta})\bigr\} \ell^2 \delta \tag{Step 2} \\
& \geq \frac{r (1 - 2\delta)\sqrt{2\pi}}{\rho L\sqrt{d + 2}} \min\bigl\{\wt{\pi}_{\nu,r}(\mc{S}),\wt{\pi}_{\nu,r}(\mc{R})\bigr\}   \ell^2 \delta (1 - a). \tag{by hypothesis}
\end{align*}
Setting $\delta = 1/3$, we have
\begin{equation*}
\wt{\Phi}_{\nu,r}(\mc{S}) \geq \min\biggl\{\frac{\sqrt{2\pi} r}{9\sqrt{d + 2} \rho L} \ell^2(1 - a), \frac{a\ell}{6}\biggr\}
\end{equation*}
and putting $a = r\ell/(2\rho)$ yields the claim.

Now, we turn to establishing the inequalities used in the above chain.

\paragraph{Step 1: Lower bound the ergodic flow.}
By symmetry, $\wt{Q}_{\nu,r}(\mc{S}_1,\mc{S}_2) = \wt{Q}_{\nu,r}(\mc{S}_1,\mc{S}_2)$, whence a direct computation yields
\begin{equation*}
2\wt{Q}_{\nu,r}(\mc{S}_1,\mc{S}_2) = \wt{Q}_{\nu,r}(\mc{S}_1,\mc{S}_2) + \wt{Q}_{\nu,r}(\mc{S}_2,\mc{S}_1) \geq \delta \wt{\pi}_{\nu,r}(\mc{S}_{\delta}).
\end{equation*}

\paragraph{Step 2: Estimate the stationary distribution.}

Both the upper and lower  bounds on $\wt{\pi}_{\nu,r}(\mc{S})$ are a direct consequence of the following inequalities:
\begin{equation*}
\ell \nu_d r^d \nu(\mc{S})  \leq {J}_{\nu,r}(\mc{S}) \leq \nu_d r^d \nu(\mc{S}).
\end{equation*}
\paragraph{Step 3: Isoperimetric inequality.}
NB: the proof of Lemma \ref{lem: nonconvex_isoperimetry} from first principles is non-trivial, even when the domain $\mc{C}_{\sigma}$ is itself convex, and is a primary technical contribution of the seminal work \textcolor{red}{(Lovasz 1990)}, extended by \textcolor{red}{(Dyer 1991)} among others. However, once the result is shown in the convex setting, it is not hard to show that it applies to Lipschitz transformations of convex sets as well.
\begin{proof}[Proof of Lemma \ref{lem: nonconvex_isoperimetry}]
	For $\Omega_i, i = 1,2,3$, denote the preimage
	\begin{equation*}
	R_i = \set{x \in \mathcal{K}: g(x) \in \Omega_i}
	\end{equation*}
	For any $x \in R_1, y \in R_2$, 
	\begin{equation*}
	\norm{x - y} \geq \frac{1}{L}\norm{g(x) - g(y)} \geq \frac{1}{L} \dist(\Omega_1, \Omega_2). 
	\end{equation*}
	Since $x \in \Omega_1$ and $y \in \Omega_2$ were arbitrary, we have
	\begin{equation*}
	\dist(R_1, R_2) \geq \frac{1}{L} \dist(\Omega_1, \Omega_2).
	\end{equation*}
	By Theorem 2.2 of \textcolor{red}{(Lovasz 1990)},
	\begin{align*}
	\nu(R_3) & \geq 2\frac{\dist(R_1, R_2)}{\rho} \min \{\nu(R_1), \nu(R_2)\} \\
	& \geq \frac{2}{\rho L} \dist(\Omega_1, \Omega_2) \min\{\nu(R_1), \vol(R_2)\}
	\end{align*}
	and by the measure-preserving property of $g$, this implies
	\begin{equation*}
	\nu(\Omega_3) \geq\frac{2}{\rho L} \dist(\Omega_1, \Omega_2) \min\{\nu(\Omega_1), \nu(\Omega_2)\}.
	\end{equation*}
\end{proof}

\paragraph{Step 4: Total variation distance.}

\begin{proof}[Proof of Lemma~\ref{lem: one_step_distributions}]
	Note that~\eqref{eqn:one_step_distributions_2} follows from~\eqref{eqn:one_step_distributions_1} by first taking the supremum over all $\mc{S} \subseteq \mc{C}_{\sigma}$, and then the infimum over all $x \in \mc{S}_1$ and $y \in \mc{S}_2$.

>>>>

\documentclass{article}
\usepackage{amsmath}
\usepackage{amsfonts, amsthm, amssymb}
\usepackage{graphicx}
\usepackage[colorlinks]{hyperref}
\usepackage[parfill]{parskip}
\usepackage{algpseudocode}
\usepackage{algorithm}
\usepackage{enumerate}
\usepackage[shortlabels]{enumitem}
\usepackage{fullpage}

@@

\newcommand{\eqdist}{\ensuremath{\stackrel{d}{=}}}
\newcommand{\Graph}{\mathcal{G}}
\newcommand{\Reals}{\mathbb{R}}
\newcommand{\Identity}{\mathbb{I}}
\newcommand{\distiid}{\overset{\text{i.i.d}}{\sim}}
\newcommand{\convprob}{\overset{p}{\to}}
\newcommand{\convdist}{\overset{w}{\to}}
\newcommand{\Expect}[1]{\mathbb{E}\left[ #1 \right]}
\newcommand{\Risk}[2][P]{\mathcal{R}_{#1}\left[ #2 \right]}
\newcommand{\Prob}[1]{\mathbb{P}\left( #1 \right)}
\newcommand{\iset}{\mathbf{i}}
\newcommand{\jset}{\mathbf{j}}
\newcommand{\myexp}[1]{\exp \{ #1 \}}
\newcommand{\norm}[1]{\left\lVert#1\right\rVert}
\newcommand{\abs}[1]{\left \lvert #1 \right \rvert}
\newcommand{\restr}[2]{\ensuremath{\left.#1\right|_{#2}}}
\newcommand{\ext}[1]{\widetilde{#1}}
\newcommand{\set}[1]{\left\{#1\right\}}
\newcommand{\seq}[1]{\set{#1}_{n \in \N}}
\newcommand{\dotp}[2]{\langle #1, #2 \rangle}
\newcommand{\floor}[1]{\left\lfloor #1 \right\rfloor}
\newcommand{\Var}{\mathrm{Var}}
\newcommand{\diam}{\mathrm{diam}}

\newcommand{\emC}{C_n}
\newcommand{\emCpr}{C'_n}
\newcommand{\emCthick}{C^{\sigma}_n}
\newcommand{\emCprthick}{C'^{\sigma}_n}
\newcommand{\emS}{S^{\sigma}_n}
\newcommand{\estC}{\widehat{C}_n}
\newcommand{\hC}{\hat{C^{\sigma}_n}}
\newcommand{\vol}{\text{vol}}
\newcommand{\spansp}{\mathrm{span}~}
\newcommand{\1}{\mathbf{1}}

\newcommand{\Linv}{L^{\dagger}}

\DeclareMathOperator*{\argmax}{argmax}

\newcommand{\emF}{\mathbb{F}_n}
\newcommand{\emG}{\mathbb{G}_n}
\newcommand{\emP}{\mathbb{P}_n}
\newcommand{\F}{\mathcal{F}}
\newcommand{\D}{\mathcal{D}}
\newcommand{\R}{\mathcal{R}}
\newcommand{\Rd}{\Reals^d}

%%% Data
\newcommand{\Xbf}{X}

%%% Vectors
\newcommand{\thetast}{\theta^{\star}}

%%% Matrices
\newcommand{\X}{X} % no bold
\newcommand{\Y}{Y} % no bold
\newcommand{\Z}{Z} % no bold
\newcommand{\Lgrid}{L_{\grid}}
\newcommand{\Dgrid}{D_{\grid}}
\newcommand{\Linvgrid}{L_{\grid}^{\dagger}}

%%% Sets and classes
\newcommand{\Xset}{\mathcal{X}}
\newcommand{\Sset}{\mathcal{S}}
\newcommand{\Cset}{\mathcal{C}}
\newcommand{\Csig}{\Cset_{\sigma}}
\newcommand{\Hclass}{\mathcal{H}}
\newcommand{\Pclass}{\mathcal{P}}

%%% Distributions and related quantities
\newcommand{\Pbb}{\mathbb{P}}
\newcommand{\Ebb}{\mathbb{E}}
\newcommand{\Qbb}{\mathbb{Q}}

%%% Vector spaces
\newcommand{\Zbb}{\mathbb{Z}}

%%% Operators
\newcommand{\Tadj}{T^{\star}}
\newcommand{\dive}{\mathrm{div}}
\newcommand{\dif}{\mathop{}\!\mathrm{d}}
\newcommand{\gradient}{\mathcal{D}}
\newcommand{\Hessian}{\mathcal{D}^2}

%%% Misc
\newcommand{\grid}{\mathrm{grid}}
\newcommand{\critr}{R_n}
\newcommand{\dx}{\,dx}
\newcommand{\dy}{\,dy}
\newcommand{\dr}{\,dr}
\newcommand{\wt}[1]{\widetilde{#1}}

@@

\begin{document}
\title{Notes for 9/16/19 - 9/20/19}
\author{Alden Green}
\date{\today}
\maketitle

In the local spectral density clustering problem, one observes data $x_1,\ldots,x_n$ sampled independently from a density function $f$ supported on $\mathcal{X}$. Letting $\Cset$ be a connected component of the upper level set $\set{x:f(x) > \lambda}$, since we observe a finite sample we can only hope to recover $\Csig = \Cset + B(0,\sigma)$ for some $\sigma > 0$. Our strategy will be to
\begin{itemize}
	\item Form a neighborhood graph $G_{n,r}$ by connecting points at scale $r$ (i.e. using the kernel function $\1(\norm{x - y} \leq r)$. 
	\item Operate in some manner on the neighborhood graph $G_{n,r}$ to form a cluster estimate $\hat{C}$. 
\end{itemize}

This week, we focus on lower bounds for the density clustering problem. To begin, let's detail the various lower bounds one might hope to prove (roughly in order from weakest to strongest.) In the following, $\Sset[\Xbf]$ will always be a set with high symmmetric set difference metric to $\Csig[\Xbf]$. For example, assume $\Delta(\Sset[\Xbf],\Csig[\Xbf]) \geq 1/8$ with high probability as $n \to \infty$. All but the last lower bound are inconsistency statements for various classes of algorithms; the last lower bound is a statement regarding sample complexity.
\begin{enumerate}
	\item There exists some $\Sset \subset \mathcal{X}$ such that if you perform PPR over $G_{n,r}$, and tune hyperparameters appropriately for $\Sset$, with high probability you will recover $\Sset[\Xbf]$ as $n \to \infty$.

	\item There exists some $\Sset \subset \mathcal{X}$ such that if you perform PPR over $G_{n,r}$, and tune hyperparameters appropriately for $\Csig$, with high probability you will recover $\Sset[\Xbf]$ as $n \to \infty$.

	\item If you perform PPR over $G_{n,r}$ with $r$ tuned appropriately for $\Csig$, for any choice of hyperparameters $v, \alpha$ and $\pi_0$, with high probability you will recover some $\Sset_{(v,\alpha,\pi_0)}[\Xbf]$ as $n \to \infty$.

	\item If you perform PPR over $G_{n,r}$ for any choice of hyperparameters $r, v, \alpha$ and $\pi_0$, with high probability you will recover some $\Sset_{(r, v,\alpha,\pi_0)}[\Xbf]$ as $n \to \infty$.

	\item If you perform any spectral algorithm over $G_{n,r}$, you will fail to recover $\Csig[\Xbf]$ as $n \to \infty$.

	\item For a fixed $n$ and for any $r > 0$, any algorithm operating on $G_{n,r}$ will have $\Delta(\widehat{C}, \Csig[\Xbf]) > \eta$ for some critical radius $\eta$ which may depend on $n$ and $r$. 
\end{enumerate}

The first lower bound is very weak, and we do not investigate it further. We include it merely to note that the strategy of applying an upper bound on PPR misclassification error to an appropriately chosen $\Sset \subset \Xset$ would result in this type of weak lower bound. Our lower bound will therefore require at least in part different proof techniques than the one we use for our upper bound.

\section{PPR with any hyperparameters.}

\section{Any spectral algorithm.}

Note: this section will be consistent in spirit, but not in technical details, with the problem as introduced previously.

Let $K(x,y)$ be a positive semi-definite kernel function in $\Rd$.
